Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-07 Draft/Draft.Rmd
EDITS

---
title: Plant-pollintor networks worldwide are composed by the same specific building
  blocks
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
bibliography: bibliography.bib
---

@@

We have compiled 60 plant-pollinator networks from 18 different studies (Table S1). All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength. In total, there were 503 plant species, 1111 pollinator species and 6248 of pairwise interactions registered. For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].

@@

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(lme4)
library(nlme)
library(tidyverse)
library(stringi)
library(ggpubr)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8, fig.cap="Figure 3. . Comparison of the motif frequencies between empirical and simulated networks collapsing the networks nodes by functional plant and pollinator functional groups. Mean percentiles close to 0 and 1 indicate under- and over- representation respectively."}

@@

Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions. The different motif positions are dividied by the average path length clasification by @simmons2020

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
##############################
#TABLE S1. List of studies
##############################

@@

references %>%
  arrange(`First author`)%>%
  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),caption = "Table S1. List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = c("left"))

>>>>

---
title: Plant-pollintor networks worldwide are composed by the same specific building
  blocks
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
bibliography: bibliography.bib
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

@@

We have compiled 60 plant-pollinator networks from 18 different studies (Table S1). All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength. In total, there were 503 plant species, 1,111 pollinator species and 6248 of pairwise interactions registered. For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].

@@

Condense and summarize information

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = 'center',fig.width=6,fig.height=3.5}
library(lme4)
library(nlme)
library(tidyverse)
library(stringi)
library(ggpubr)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="Figure 3. Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions. The different motif positions are dividied by the average path length clasification by @simmons2020."}

@@

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
##############################
#TABLE S1. List of studies
##############################

@@

references %>%
  arrange(`First author`)%>%
  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),caption = "Table S1. List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = c("center"))

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12}
setwd("~/R_Projects/Reproductive Traits")

library(kableExtra)

library(dplyr)
library(readxl) #read excel file (trait data)
library(dplyr) #data manipulation
library(visdat) #VISUALIZE MISSING DATA
library(naniar)
library(tidyverse)
########################################################################################################################################################
#1) READ TRAIT DATA
########################################################################################################################################################

Trait <- c("Plant height (m)", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovules per flower",
           "Flowers per plant",  "Autonomous selfing (fruit set)")

Trait1 <- c("Lifepan", "Life form", "Flower shape", "Flower symmetry", "Autonomous selfing", "Compatibility system", "Breeding system", "")

T.cat <- linebreak(c("Short-lived \n Perennial", "Herb \n Shrub \n Tree", "Brush \n Campanulate \n Capitulum \n Open \n Papilionaceous \n Tube",  "Actinomorphic \n Zygomorphic", "None \n Low \n Medium \n High", "Self-incomp. \n Partially self-comp. \n Self-comp.", "Hermaphrodite \n Monoecious \n Dioecious",""),align = c("l"))

Type <- c("Vegetative", "Floral", "Floral", "Floral", "Floral", "Floral", "Floral","Reproductive")

Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive", "")

dat <- data.frame(Type, Trait,Type_1, Trait1)

colnames(dat) <- c("Type","Traits","Type", "Traits")

kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "Table S2. Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
kable_styling(full_width = F) %>%
add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)
